---
title: "NDVI Linear regression model"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---

```{r}
#import the data
library(readr)
ndvi <- read_csv("data/ndvi.csv")
head(ndvi) #to view the head of th data
```

we want a linear regression model based on this formula Biomass = B0 + B1\*NDVI

```{r}
#we can visualise the linear relationship between the NDVI and the BIOMASS with a scatterplot
plot(x = ndvi$NDVI, y = ndvi$Biomass, main = "biomass ~ NDVI",
     xlab = "NDVI", ylab = "Biomass",
     pch = 10, frame = TRUE)
abline(lm(Biomass ~ NDVI, data = ndvi), col = "blue")
      
# scatterplot
```

We can compute the correlation between the two variables

```{r}
cor.test(ndvi$Biomass, ndvi$NDVI)
```

Our correlation is too closer to 0. So there is no correlation between the two variables.

[Here](https://statisticsbyjim.com/basics/correlations/#:~:text=A%20correlation%20between%20variables%20indicates,change%20in%20a%20specific%20direction.&text=For%20example%2C%20height%20and%20weight,weight%20also%20tends%20to%20increase.) we find how to explain the correlations

We can force to make the linear model but it will not be really significant. But anyway let's try.

```{r}
#Our formula is Biomass = B0 + B1*NDVI
mbao_model <- lm(Biomass ~ NDVI , data = ndvi)# the formula
#we will print the model
mbao_model

```

Now that we have built the linear model, we also have established the relationship between the predictor and response in the form of a mathematical formula for biomass as a function for ndvi. For the above output, you can notice the 'Coefficients' part having two components: *Intercept*: 0.6774, *NDVI*: 1.9443. These are also called the beta coefficients. In other words,**\
**Biomass= Intercept + (β ∗ NDVI)

Our model is:

Biomass = 0.6674 + 1.9443\* NDVI

Before using our regression model, we have to ensure that it is statistically significant. We will print it summary to check.

```{r}
summary(mbao_model)

```

We only have to check the p-value for the statistical significance. The p-Value is very important because, We can consider a linear model to be statistically significant only when both these p-Values are less that the pre-determined statistical significance level, which is ideally 0.05.

In our case the p-value is 0.244, greater than 0.05.

Our model is not significant statistically.
